Land-use legacies and high oak resilience to drought show how the ecological and geographical rear edges do not necessarily meet today

### 2020-03-09 man/ecosystems/ms_ecosystems.Rmd
update

---
title: "Oak resilience to drought and land use show how the ecological and geographical rear edges do not necessarily meet today"
output:
  word_document: 
    fig_caption: yes
    fig_height: 6
    highlight: null
    reference_docx: ../../templates/template_ms.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecosystems.csl
---

>>>>

---
title: "Land-use legacies and high oak resilience to drought show how the ecological and geographical rear edges do not necessarily meet today"
output:
  word_document: 
    fig_caption: yes
    fig_height: 6
    highlight: null
    reference_docx: ../../templates/template_ms.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecosystems.csl
---
